Predicting the 2024 U.S. Presidential Election: A Data-Driven Analysis of Swing State Outcomes

### 2024-11-04 paper/paper.qmd
Add survey to paper
final ediing of papr and file structure, update readme and requirements

---
title: "Predicting the 2024 U.S. Presidential Election: A Data-Driven Analysis of Swing State Outcomes"
subtitle: "Forecast Model Suggests Harris as the Probable Winner of the majority of swing states"
author: "Alexander Guarasci & Jacob Gilbert"
date: today
date-format: long
bibliography: references.bib
execute:
  echo: false
format: pdf
fig-pos: "H"
abstract: |
 This paper develops a predictive model for the 2024 U.S. Presidential Election, analyzing state-level polling data to forecast outcomes between Donald Trump and Kamala Harris. Using logistic regression, the model estimates the likelihood of Trump’s success in swing states by weighting polls based on recency and sample size. Findings indicate that Harris has a higher probability of winning in most swing states, though close margins suggest targeted campaign efforts could alter outcomes in pivotal areas. This analysis provides insight into electoral dynamics, highlighting how data-driven approaches can clarify potential election outcomes and inform strategic political decision-making.
---

@@

# 2.1 Measurement
The voter support data used in this analysis comes from raw polling information sourced from the Project 538 online database [@FiveThirtyEight]. This dataset provides predictions for candidate support for the 2024 U.S. Presidential Election by aggregating various polls that capture public sentiment toward candidates Donald Trump and Kamala Harris. Each entry in the dataset corresponds to a specific question about voting preference in a poll conducted by different polling organizations, which measures the percentage of respondents expressing their support for each candidate in their respective state. the surveys utilized one or multiple of the following methods for response gathering: Online Ad, Online Panel, Live Phone, text-to-web, mail-to-web, email, Probability panel, IVR. The diversity of the methods of collection supplies a colourful array of polls capturing all facets of voters.

@@

# 2.2 The Dataset
A swing state in the context of a US election is defined as "a state where the number of Democratic and Republican voters is about the same, that has an important influence on the result of the election of the United States President". States that do not fall under this definition are not likely to "swing" to another party as we approach the election, and thus their outcome can be reasonably assumed. Thus the election result is normally decided by which party wins just a handful of states in the electoral college system. By concentrating on these swing states, we aim to capture the most critical and uncertain areas of the electoral map, where voter preferences are most likely to sway the final result. Thus our analysis restricts the datasets to state-level polls in the following states: Arizona, Pennsylvania, North Carolina, Georgia, Nevada, Michigan, and Wisconsin; determined to be swing states in 2024 [@nyt_swing, @FiveThirtyEight]. In @Fig-1 we see the current distribution of electoral votes that each party hold according to those sources as of October 20th, with the remaining swing states, seen in the middle of this graph set to determine if either Harris or Trump receives over 270th electoral votes.

```{python}
#| ccho: false
#| label: Fig-1
#| fig-cap: "This figure shows the cumulative total of electoral votes by state, grouped by current party affiliation, accordng to 538. The chart distinguishes between Democrat, Republican, and swing states, with a color-coded fill under each party’s cumulative curve. Key threshold of 270 electoral vote mark needed to secure a victory is diplayed. This visualization shows the democrats lead with 227 votes and the Republicans with 219 votes secured."
# Define states and electoral votes, ensuring votes are listed in reverse for clarity in plot

@@

plt.figure(figsize=(18, 14))
stop = 320
plt.step(x[:stop], cumulative_votes[:stop], where='post', color='navy', linewidth=2, marker='o')
x_reversed = np.flip(x)
plt.step(x_reversed, cumulative_votes_reversed, where='post', color='red', linewidth=2, marker='o')

@@

# Adding threshold line and markers
plt.xticks(range(len(states)), states, rotation=90, fontsize=13)
plt.axhline(270, color='purple', linestyle='--', linewidth=2)
plt.text(len(states) / 2, 275, '270 votes to win', horizontalalignment='center', color='purple', fontsize=12)
plt.xlabel('Electoral College by State', fontsize=15)
plt.ylabel('Total Votes', fontsize=15)
plt.title('Cumulative Electoral Votes by State', fontsize=25)
plt.grid(True, linestyle='--', alpha=0.5)
plt.tight_layout()
plt.show()

@@

In keeping with this aim, we focused our analysis on polls conducted after September. Early in the election cycle, polls can be significantly influenced by initial campaign events, such as the shocks from the first debates or unexpected changes in the candidate lineup. For example, Joe Biden dropping out as a candidate on July 21st severely impacted the odds of a Kamala Harris victory. These factors can introduce biases and fluctuations that do not necessarily reflect the enduring preferences of the electorate. By selecting polls from after September, we capture data from a period when voter opinions are more stable and better represent the current state of the race.

```{python}

#| echo: false
#| label: Fig-2
#| fig-cap: "Summary statistics of key sample variabls by state. Shows high sampl size and numeric grade among all polls of swing states."

@@

# Print the table using tabulate
print(tabulate(rows, headers=['State', 'Variable', 'Mean', 'Std', 'Min', 'Max', 'Count'], tablefmt='simple_grid'))
```
**Figure 2: Summary statistics of key sample variables by state. Shows high sample size and numeric grade among all polls of swing states.**

# 2.3 Variables of Interest
In our logistic regression model predicting the 2024 U.S. Presidential Election outcome, the primary variables of interest are derived from aggregated state-level polling data. The percentage of respondents favouring a candidate is the key variable used for prediction. Within the collection of polls in our sample, the independent variable `trump_pct` represents the percentage of respondents who indicate support for Donald Trump, and `harris_pct` respectively.

Polls are taken towards the build-up of an election and thus are taken by respondents at different times. @Fig-2 shows how the sample of polls are distributed over time in which it is clear that we have a collection of polls from a wide range of periods. Because sentiment changes over time we adjust the weight that we place on polls that are closer to the election as these are more indicative of how respondents will be voting on the day.

@@

Another aspect of the polls we wish to consider is the population size of each. Larger polls result in a stronger reduction in randomness in the response. The larger the sample size the more the response reflects the true population of the state, this is known as the law of large numbers. In @Fig-3 we can see the variety within the state polls.
For use in the model, the percentages in these polls are weighted for recency and size of the sampled population.

@@

# 4 Results {#sec-results}
## Regression results

```{python}
#| echo: false
#| label: Fig-4
# Data setup
data = {
    'State': ['Arizona', 'Georgia', 'Michigan', 'Nevada', 'North Carolina', 'Pennsylvania', 'Wisconsin'],
    'Trump %': [49.85, 49.39, 48.57, 47.9, 48.48, 47.68, 47.76],
    'Trump SD': [1.24, 1.78, 2.14, 1.5, 1.41, 1.81, 2.0],
    'Harris %': [47.04, 47.66, 47.72, 48.63, 48.58, 48.53, 48.92],
    'Harris SD': [2.17, 2.52, 2.12, 1.19, 1.55, 1.29, 1.72],
    'Trump Winning %': [86.85, 71.18, 53.09, 21.34, 32.31, 19.67, 15.52]
}

@@

# Display as a professional table
print(tabulate(
    df, headers='keys', tablefmt='grid', showindex=False,
    floatfmt=(".2f", ".2f", ".2f", ".2f", ".2f", ".2f")
))

@@

```{python}
#| echo: false
#| label: Fig-5
#| fig-cap: "A centered bar chart where each state has a bar reflecting Trump’s probability of winning. The bars extend to the right or left from the center line at 50%, with the distance representing the magnitude of deviation from an even chance. This chart visualizes Trump’s relative strength in each swing state and highlights that he s only favoured in Georgia and Arizona."
# Data setup (can adjust based on model results)
data = {
    'State': ['Arizona', 'Georgia', 'Michigan', 'Nevada', 'North Carolina', 'Pennsylvania', 'Wisconsin'],
    'Trump % (Mean)': [49.85, 49.39, 48.57, 47.9, 48.48, 47.68, 47.76],
    'Trump % (SD)': [1.24, 1.78, 2.14, 1.5, 1.41, 1.81, 2.0],
    'Harris % (Mean)': [47.04, 47.66, 47.72, 48.63, 48.58, 48.53, 48.92],
    'Harris % (SD)': [2.17, 2.52, 2.12, 1.19, 1.55, 1.29, 1.72],
    'Trump Win Probability (%)': [86.85, 71.18, 53.09, 21.34, 32.31, 19.67, 15.52]
}
df = pd.DataFrame(data)
df['Distance from 50%'] = df['Trump Win Probability (%)'] - 50

@@

Kamala is predicted to win the remaining states and is given fairly high chances of locking these up. despite only winning Nevada, North Carolina and Pennsylvania by under a percentage point in the model Kamala's probability of winning those electoral votes is very high. This is due to the small standard deviations shown in @Fig-4 making the predicted outcome of a victory more secure.

@@

Taking The probabilities from the model above we can look at the outcomes of the 207 possible combinations of wins and losses for Trump in these swing states and deduce his overall probability of reaching 270 electoral votes. Based on the modelled probabilities his current expected vote is 41.05, below the threshold of 51 he needs based on our assumptions.

@@

The result of the model tells us that overall the polls in October are favouring Harris to win the election. From the perspective of the republican party if they wish to "turn the tide" this model highlights which of the swing states are more likely to flip than others. North Carolina is the premier state predicted to go blue with the highest likelihood of Trump winning. It would be recommended to allocate resources here to try and win a state from Harris. As far as retaining currently favoured states, Michigan is in a weak position for Trump according to the model, nearing a coin flip. As this state holds 15 electoral College votes, the 4th most of the swing states, it is a key state to win. Assuming the model's correct prediction that Michigan is currently held by Trump, expect the Democrats to attempt to tip the scales in their favour there.

One of the most significant insights from this analysis is the discrepancy between polling data and the betting markets. While the majority of reputable polls suggest that Kamala Harris is favoured on both a national level and in most swing states, betting markets like Polymarket imply a 67% chance of Trump winning the election as of October 23, 2024 [@polymarket]. This stark disconnect raises questions about the accuracy of traditional polling methods and whether betting markets, which are financial tools driven by market forces, may offer a more precise reflection of public sentiment.

@@

Another important consideration is the possible biases in both polling and betting markets. Poll respondents may not be a representative sample of the electorate; for example, Democrats could be more likely to respond to polls, skewing the results in favour of Harris. Meanwhile, individuals who participate in betting markets might form a subset of the population that is disproportionately supportive of Trump, which could explain why the implied odds heavily favour him. Furthermore, the rapid expansion and increased liquidity of betting markets in the last few years may have improved their efficiency, making them more reflective of real-world probabilities. However, historical data still suggest that polls have been accurate 78% of the time in predicting elections [@FiveThirtyEight], indicating that the reliability of betting markets remains questionable, especially in light of their poor performance during the 2016 election, when Trump’s odds were listed at +475 (17%) just before his victory [@oddsshark2016].

@@

While our model provides a structured framework for predicting the election, it has several limitations. First, the model is based on polling data available far in advance of the election, meaning there is a high degree of uncertainty, and the model may not fully capture late shifts in public opinion or external shocks (e.g., economic downturns or scandals). As polling results are based on public opinion, large shock events are expected, furthermore, scheduled events such as debates and rallies can be expected to have large impacts on the election that cannot be modelled here. Additionally, the use of linear modelling may oversimplify the complex dynamics of voter behaviour, as elections often involve nonlinear influences that are difficult to predict.

@@

Ultimately, while our model offers a strong foundation for predicting the 2024 U.S. Presidential Election, there is still much to learn. By refining the model and incorporating additional data, we can move closer to producing predictions that more accurately reflect voter behaviour and election outcomes.

# Appendix A: Idealized Methodology and Survey for Forecasting the US Presidential Election with Incentivized Betting

@@

A betting pool is a central part of this methodology, with $50,000 allocated as rewards for respondents who accurately predict the election outcome. Each participant will receive a $10 allowance to bet on their predicted winner (Trump or Harris), with payouts based on live odds, creating a direct incentive for respondents to make thoughtful, informed predictions. The purpose of this is twofold, it aims to minimize the attrition of the respondents, so that more people complete the survey, and it also will provide us insight into who people think will win rather than just who people want to win. Ideally, the purpose of this is so that people take into consideration who their friends, family, and their community, are expecting to win.

@@

# Appendix B: Siena / New York Tims Pennsylvania poll

@@

- Statehouse district
- Political party affiliation
- Race
- Gender
- Marital status
- Household size
- Turnout history
- Age
- Home ownership
The sampling is conducted in order to address telephone coverage around the state as well as nonresponse rates. Records are selected by state and sampling is separated for Pennsylvania as a whole and its major city Philadelphia. The voter file is then ratified and weights are based on historically modelled response rate and coverage.

>>>>

---
title: "Predicting the 2024 U.S. Presidential Election: A Data-Driven Analysis of Swing State Outcomes"
subtitle: "Forecast Model Suggests Harris as the Probable Winner of the majority of swing states"
author: "Alexander Guarasci & Jacob Gilbert"
date: today
date-format: long
bibliography: references.bib
execute:
  echo: false
format: pdf
fig-pos: "H"
abstract: |
 This paper develops a predictive model for the 2024 U.S. Presidential Election, analyzing state-level polling data to forecast outcomes between Donald Trump and Kamala Harris. Using logistic regression, the model estimates the likelihood of Trump’s success in swing states by weighting polls based on recency and sample size. Findings indicate that Harris has a higher probability of winning in most swing states, though close margins suggest targeted campaign efforts could alter outcomes in pivotal areas. This analysis provides insight into electoral dynamics, highlighting how data-driven approaches can clarify potential election outcomes and inform strategic political decision-making.
thanks: "Code and data supporting this analysis is available at: https://github.com/JfpGilbert0/nov_2024_trump_v_harris"
---

@@

# 2.1 Measurement
The voter support data used in this analysis comes from raw polling information sourced from the Project 538 online database [@FiveThirtyEight]. This dataset provides predictions for candidate support for the 2024 U.S. Presidential Election by aggregating various polls that capture public sentiment toward candidates Donald Trump and Kamala Harris. Each entry in the dataset corresponds to a specific question about voting preference in a poll conducted by different polling organizations, which measures the percentage of respondents expressing their support for each candidate in their respective state. The surveys utilized one or multiple of the following methods for response gathering: Online Ad, Online Panel, Live Phone, text-to-web, mail-to-web, email, Probability panel, IVR. The diversity of the methods of collection supplies a colorful array of polls capturing all facets of voters.

@@

# 2.2 The Dataset
A swing state in the context of a US election is defined as "a state where the number of Democratic and Republican voters is about the same, that has an important influence on the result of the election of the United States President" (@oxfordlanguages). States that do not fall under this definition are not likely to "swing" to another party as we approach the election, and thus their outcome can be reasonably assumed. Thus the election result is normally decided by which party wins just a handful of states in the electoral college system. By concentrating on these swing states, we aim to capture the most critical and uncertain areas of the electoral map, where voter preferences are most likely to sway the final result. Thus our analysis restricts the datasets to state-level polls in the following states: Arizona, Pennsylvania, North Carolina, Georgia, Nevada, Michigan, and Wisconsin; determined to be swing states in 2024 [@nyt_swing, @FiveThirtyEight]. In @Fig-1 we see the current distribution of electoral votes that each party holds according to those sources as of October 20th, with the remaining swing states, seen in the middle of this graph, set to determine if either Harris or Trump receives over 270th electoral votes.

```{python}
#| ccho: false
#| label: Fig-1
#| fig-cap: "This figure shows the cumulative total of electoral votes by state, grouped by current party affiliation, according to 538. The chart distinguishes between Democrat, Republican, and swing states, with a color-coded fill under each party’s cumulative curve. Key threshold of 270 electoral vote marks needed to secure a victory is displayed. This visualization shows the democrats lead with 227 votes and the Republicans with 219 votes secured."
# Define states and electoral votes, ensuring votes are listed in reverse for clarity in plot

@@

stop_index_forward = np.argmax(cumulative_votes >= 320)
stop_index_reverse = np.argmax(cumulative_votes_reversed >= 312)

plt.figure(figsize=(18, 14))
plt.step(x[:stop_index_forward+1], cumulative_votes[:stop_index_forward+1], where='post', color='navy', linewidth=2, marker='o')
x_reversed = np.flip(x)
plt.step(x_reversed[:stop_index_reverse + 1], cumulative_votes_reversed[:stop_index_reverse + 1], where='post', color='red', linewidth=2, marker='o')

@@

# Adding threshold line and markers
plt.xticks(range(len(states)), states, rotation=90, fontsize=15)
plt.axhline(270, color='purple', linestyle='--', linewidth=2)
plt.text(len(states) / 2, 275, '270 votes to win', horizontalalignment='center', color='purple', fontsize=12)
plt.xlabel('Electoral College by State', fontsize=15)
plt.ylabel('Total Votes', fontsize=15)
plt.title('Cumulative Electoral Votes by State', fontsize=25)
plt.grid(True, linestyle='--', alpha=0.5)
plt.tight_layout()
plt.show()

@@

In keeping with this aim, we focused our analysis on polls conducted after September. Early in the election cycle, polls can be significantly influenced by initial campaign events, such as the shocks from the first debates or unexpected changes in the candidate lineup. For example, Joe Biden dropping out as a candidate on July 21st severely impacted the odds of a Kamala Harris victory. These factors can introduce biases and fluctuations that do not necessarily reflect the enduring preferences of the electorate. By selecting polls from after September, we capture data from a period when voter opinions are more stable and better represent the current state of the race. All data was gathered on October 24th 2024 and thus all data and analysis is based on what the polling data reflects at this point in time. @Fig-2 show a general overview of the polling data.

\newpage
```{python}
#| echo: false

@@

# Print the table using tabulate
print(tabulate(rows, headers=['State', 'Variable', 'Mean', 'Std', 'Min', 'Max', 'Count'], tablefmt='simple_grid'))

```
```{python}
#| echo: false
#| label: Fig-2
# This code block exits for the use of self referencing
print(tabulate(rows, headers=['State', 'Variable', 'Mean', 'Std', 'Min', 'Max', 'Count'], tablefmt='simple_grid'))
```
**Figure 2: Summary statistics of key sample variables by state. Shows high sample size and numeric grade among all polls of swing states.**

# 2.3 Variables of Interest
In our logistic regression model predicting the 2024 U.S. Presidential Election outcome, the primary variables of interest are derived from aggregated state-level polling data. The percentage of respondents favoring a candidate is the key variable used for prediction. Within the collection of polls in our sample, the independent variable `trump_pct` represents the percentage of respondents who indicate support for Donald Trump, and `harris_pct` respectively.

Polls are taken towards the build-up of an election and thus are taken by respondents at different times. @Fig-3 shows how the sample of polls are distributed over time in which it is clear that we have a collection of polls from a wide range of periods. Because sentiment changes over time we adjust the weight that we place on polls that are closer to the election as these are more indicative of how respondents will be voting on the day.

@@

Another aspect of the polls we wish to consider is the population size of each. Larger polls result in a stronger reduction in randomness in the response. The larger the sample size the more the response reflects the true population of the state, this is known as the law of large numbers. In @Fig-2 we can see the variety within the state polls.
For use in the model, the percentages in these polls are weighted for recency and size of the sampled population.

@@

\newpage
# 4 Results {#sec-results}
## Regression results

```{python}
#| echo: false
# Data setup
data = {
    'State': ['Arizona', 'Georgia', 'Michigan', 'Nevada', 'North Carolina', 'Pennsylvania', 'Wisconsin'],
    'Trump %': [49.85, 49.39, 48.57, 47.9, 48.48, 47.68, 47.76],
    'Trump SD': [1.24, 1.78, 2.14, 1.5, 1.41, 1.81, 2.0],
    'Harris %': [47.04, 47.66, 47.72, 48.63, 48.58, 48.53, 48.92],
    'Harris SD': [2.17, 2.52, 2.12, 1.19, 1.55, 1.29, 1.72],
    'Trump Winning %': [86.85, 71.18, 53.09, 21.34, 32.31, 19.67, 15.52]
}

@@

# Display as a professional table
print(tabulate(
    df, headers='keys', tablefmt='grid', showindex=False,
    floatfmt=(".2f", ".2f", ".2f", ".2f", ".2f", ".2f")
))
```
```{python}
#| echo: false
#| label: Fig-4
# This code block exits for the use of self referencing
print(tabulate(
    df, headers='keys', tablefmt='grid', showindex=False,
    floatfmt=(".2f", ".2f", ".2f", ".2f", ".2f", ".2f")
))

@@

```{python}
#| echo: false
#| label: Fig-5
#| fig-cap: "A centered bar chart where each state has a bar reflecting Trump’s probability of winning. The bars extend to the right or left from the center line at 50%, with the distance representing the magnitude of deviation from an even chance. This chart visualizes Trump’s relative strength in each swing state and highlights that he is only favored in Georgia and Arizona."
# Data setup (can adjust based on model results)
data = {
    'State': ['Arizona', 'Georgia', 'Michigan', 'Nevada', 'North Carolina', 'Pennsylvania', 'Wisconsin'],
    'Trump % (Mean)': [49.85, 49.39, 48.57, 47.9, 48.48, 47.68, 47.76],
    'Trump % (SD)': [1.24, 1.78, 2.14, 1.5, 1.41, 1.81, 2.0],
    'Harris % (Mean)': [47.04, 47.66, 47.72, 48.63, 48.58, 48.53, 48.92],
    'Harris % (SD)': [2.17, 2.52, 2.12, 1.19, 1.55, 1.29, 1.72],
    'Trump Win Probability (%)': [86.85, 71.18, 53.09, 21.34, 32.31, 19.67, 15.52]
}
df = pd.DataFrame(data)
df['Distance from 50%'] = df['Trump Win Probability (%)'] - 50

@@

Kamala is predicted to win the remaining states and is given fairly high chances of locking these up. Despite only winning Nevada, North Carolina and Pennsylvania by under a percentage point in the model, Kamala's probability of winning those electoral votes is very high. This is due to the small standard deviations shown in @Fig-4 making the predicted outcome of a victory more secure.

@@

Taking The probabilities from the model above we can look at the outcomes of the 207 possible combinations of wins and losses for Trump in these swing states and deduce his overall probability of reaching 270 electoral votes. Based on the modeled probabilities his current expected vote is 41.05, below the threshold of 51 he needs based on our assumptions.

@@

The result of the model tells us that overall the polls in October are favoring Harris to win the election. From the perspective of the republican party if they wish to "turn the tide" this model highlights which of the swing states are more likely to flip than others. North Carolina is the premier state predicted to go blue with the highest likelihood of Trump winning. It would be recommended to allocate resources here to try and win a state from Harris. As far as retaining currently favored states, Michigan is in a weak position for Trump according to the model, nearing a coin flip. As this state holds 15 electoral College votes, the 4th most of the swing states, it is a key state to win. Assuming the model's correct prediction that Michigan is currently held by Trump, expect the Democrats to attempt to tip the scales in their favor there. Although FiveThirtyEight defines them as swing states, this model predicts Wisconsin and Arizona are fairly secure for Kamala and Trump respectively. Showing how modeling polling data is useful in predicting state results that were previously deemed uncertain.

One interesting insight from this analysis is the discrepancy between polling data and the betting markets. While the majority of reputable polls suggest that Kamala Harris is favored on both a national level and in most swing states, betting markets like Polymarket imply a 67% chance of Trump winning the election as of October 23, 2024 [@polymarket]. This stark disconnect raises questions about the accuracy of traditional polling methods and whether betting markets, which are financial tools driven by market forces, may offer a more precise reflection of public sentiment.

@@

Another important consideration is the possible biases in both polling and betting markets. Poll respondents may not be a representative sample of the electorate; for example, Democrats could be more likely to respond to polls, skewing the results in favor of Harris. Meanwhile, individuals who participate in betting markets might form a subset of the population that is disproportionately supportive of Trump, which could explain why the implied odds heavily favor him. Furthermore, the rapid expansion and increased liquidity of betting markets in the last few years may have improved their efficiency, making them more reflective of real-world probabilities. However, historical data still suggest that polls have been accurate 78% of the time in predicting elections [@FiveThirtyEight], indicating that the reliability of betting markets remains questionable, especially in light of their poor performance during the 2016 election, when Trump’s odds were listed at +475 (17%) just before his victory [@oddsshark2016].

@@

While our model provides a structured framework for predicting the election, it has several limitations. First, the model is based on polling data available far in advance of the election, meaning there is a high degree of uncertainty, and the model may not fully capture late shifts in public opinion or external shocks (e.g., economic downturns or scandals). As polling results are based on public opinion, large shock events are expected, furthermore, scheduled events such as debates and rallies can be expected to have large impacts on the election that cannot be modeled here. Additionally, the use of linear modeling may oversimplify the complex dynamics of voter behavior, as elections often involve nonlinear influences that are difficult to predict.

@@

Ultimately, while our model offers a strong foundation for predicting the 2024 U.S. Presidential Election, there is still much to learn. By refining the model and incorporating additional data, we can move closer to producing predictions that more accurately reflect voter behavior and election outcomes.

\newpage
# Appendix A: Idealized Methodology and Survey for Forecasting the US Presidential Election with Incentivized Betting {#sec-apx-A}

@@

A betting pool is a central part of this methodology, with $50,000 allocated as rewards for respondents who accurately predict the election outcome. Each participant will receive a $10 allowance to bet on their predicted winner (Trump or Harris), with payouts based on live odds, creating a direct incentive for respondents to make thoughtful, informed predictions. The purpose of this is twofold, it aims to minimize the attrition of the respondents, so that more people complete the survey, and it also will provide us insight into who people think will win rather than just who people want to win. Ideally, the purpose of this is so that people take into consideration who their friends, family, and their community are expecting to win.

@@

\newpage

# Appendix B: Siena / New York Tims Pennsylvania poll {#sec-apx-B}

@@

- Statehouse district
- Political party affiliation
- Race
- Gender
- Marital status
- Household size
- Turnout history
- Age
- Home ownership
The sampling is conducted in order to address telephone coverage around the state as well as nonresponse rates. Records are selected by state and sampling is separated for Pennsylvania as a whole and its major city Philadelphia. The voter file is then ratified and weights are based on historically modeled response rate and coverage.
